---
title: "ROI Weekly Metrics Report"
date: "Data Extracted and Report Ran: `r Sys.Date()`"
header-includes:  
    \usepackage[labelformat=empty]{caption}
    \usepackage{placeins}
    \usepackage{booktabs}
    \usepackage{pdflscape}
    
output:
  pdf_document:
    extra_dependencies: ["float"]
    toc: true
    keep_tex: yes
    fig_width: 7
    fig_height: 5
    fig_caption: true
    df_print: paged 
---


  This Weekly ROI Metrics Report contains metrics related to the return of information (ROI) and results to Connect participants including data on ROI report availability, report viewed status, and timing. Connect currently returns physical activity results to participants. Additional metrics will be added as new ROI is released. The Weekly ROI Metrics Report is run on a weekly basis and encompasses data through Monday at 10:30 AM ET.

```{r setup,eval=TRUE,include=FALSE,echo=FALSE, warning=FALSE}
#latex_engine: xelatex
library(bigrquery)
library(foreach)
library(stringr)
library(plyr)
library(epiDisplay) 
library(gmodels)
library(magrittr)
library(arsenal)
library(gtsummary)
library(rio)
library(ggplot2)
library(gridExtra)
library(scales)
library(gt)
library(tinytex)
library(data.table) 
library(tidyverse)
library(dplyr) 
library(reshape)  
library(listr) 
library(sqldf) 
library(lubridate)
library(stringr) 
library(kableExtra)
library(arsenal)
```

```{r, include=FALSE}
bq_auth()
project <- "nih-nci-dceg-connect-prod-6d04"
billing <- "nih-nci-dceg-connect-prod-6d04" ##project and billing should be consistent
```

```{r, include=FALSE}
#verified, not withdrawn consent, not deceased, 
parts <- "SELECT Connect_ID, d_794047378, d_686238347_d_446235715, d_686238347_d_749055145, d_686238347_d_295732360,
d_832139544, d_827220437, d_100767870, d_878865966, d_684635302, d_167958071, d_770257102, d_264644252, d_222161762,
d_764863765, d_195145666, d_784810139, d_517311251, d_843688458
FROM `nih-nci-dceg-connect-prod-6d04.FlatConnect.participants_JP` where Connect_ID IS NOT NULL and d_821247024 = '197316935' and d_747006172 = '104430631' and d_987563196 = '104430631' and d_536735468 = '231311385'"
parts_table <- bq_project_query(project, parts)
parts_data <- bq_table_download(parts_table, bigint = "integer64")

#pulling in physical activity data for 416831581
physical_activity <- "SELECT * FROM `nih-nci-dceg-connect-prod-6d04.ROI.physical_activity`"
physical_activity_table <- bq_project_query(project, physical_activity)
physical_activity_data <- bq_table_download(physical_activity_table, bigint = "integer64")

#merging participants table with physical activity table
PA_ROI_QC = left_join(parts_data, physical_activity_data, by = "Connect_ID")

#changing time zone of date variables to EST
PA_ROI_QC <- PA_ROI_QC %>%
  mutate(
    d_416831581 = with_tz(ymd_hms(d_416831581, tz = "UTC"), "America/New_York"),
    d_832139544 = with_tz(ymd_hms(d_832139544, tz = "UTC"), "America/New_York"),
    d_686238347_d_749055145 = with_tz(ymd_hms(d_686238347_d_749055145, tz = "UTC"), "America/New_York"),
    d_686238347_d_295732360 = with_tz(ymd_hms(d_686238347_d_295732360, tz = "UTC"), "America/New_York"),
    d_770257102 = with_tz(ymd_hms(d_770257102, tz = "UTC"), "America/New_York"),
    d_264644252 = with_tz(ymd_hms(d_264644252, tz = "UTC"), "America/New_York"),
    d_764863765 = with_tz(ymd_hms(d_764863765, tz = "UTC"), "America/New_York"),
    d_195145666 = with_tz(ymd_hms(d_195145666, tz = "UTC"), "America/New_York"),
    d_222161762 = with_tz(ymd_hms(d_222161762, tz = "UTC"), "America/New_York"),
    d_784810139 = with_tz(ymd_hms(d_784810139, tz = "UTC"), "America/New_York"))

#add filter that says because the BQ table has delays, m2 has to be completed at least 72 hrs after the current date time
PA_ROI_QC = PA_ROI_QC %>% filter(d_832139544 < Sys.time() - lubridate::hours(72))

```
\newpage

# Physical Activity Report from Module 2 Data

```{r, echo = FALSE}

#### CREATE: Report status variable ####
PA_ROI_QC <- PA_ROI_QC %>% 
  mutate(report_status = case_when(
    !is.na(d_416831581) ~ "Available",
    TRUE ~ "Unavailable"),
    report_viewed = case_when(
      d_686238347_d_446235715 == 702641611 ~ "Unread",
      d_686238347_d_446235715 == 469323437	~ "Viewed",
      d_686238347_d_446235715 == 746038746	~ "Declined"),
    site = case_when(
      d_827220437 == 531629870 ~ "HealthPartners",
      d_827220437 == 548392715 ~ "Henry Ford Health System",
      d_827220437 == 125001209 ~ "Kaiser Permanente Colorado",
      d_827220437 == 327912200 ~ "Kaiser Permanente Georgia",
      d_827220437 == 300267574 ~ "Kaiser Permanente Hawaii", 
      d_827220437 == 452412599 ~ "Kaiser Permanente Northwest",
      d_827220437 == 303349821 ~ "Marshfield Clinic Health System",
      d_827220437 == 657167265 ~ "Sanford Health",
      d_827220437 == 809703864 ~ "University of Chicago Medicine",
      d_827220437 == 517700004 ~ "National Cancer Institute",
      d_827220437 == 472940358 ~ "Baylor Scott & White Health",
      d_827220437 == 181769837 ~ "Other"),
    viewed_vs_unviewed = case_when(report_viewed == "Viewed" ~ "Viewed",
                                   report_viewed == "Declined" | report_viewed == "Unread" ~ "Unviewed"),
    muscle_strengthening = case_when(d_205380968==353358909 ~ "Yes",
                                     d_205380968==104430631 ~ "No"),
    guideline_cat = case_when(d_449038410==104593854 ~ "Not Meeting",
                              d_449038410==682636404 ~ "Meeting",
                              d_449038410==948593796 ~ "Exceeding"),
    declined_or_viewed_date = pmin(d_686238347_d_749055145, d_686238347_d_295732360, na.rm = TRUE))

PA_ROI_QC$report_viewed <- factor(PA_ROI_QC$report_viewed, levels = c(
  "Viewed",  
  "Declined",
  "Unread"))

PA_ROI_QC_t1 <- PA_ROI_QC %>% select(site, report_status)
```

```{r Table 1.1, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}

#### GENERATE TABLE 1.1: Current Physical Activity ROI Report Available Status Among Verified Participants That Submitted Module 2 #### 
create_tbl_cross1 <- function(data,row_var, colm_var, row_or_col_pct, row_name, column_name){
  cross__table <- data %>%  
    tbl_cross(
      row = !!sym(row_var),
      col = !!sym(colm_var),
      digits=c(0,2),
      percent = "row",
      missing_text="0 (0.00%)",
      label=list(!!sym(row_var) ~ row_name,
                 !!sym(colm_var) ~ column_name),
      missing="ifany",
      margin_text="Total Submitted Mod 2") %>%  as_tibble(.name_repair = "minimal")
}

comp_by_site_totals <- create_tbl_cross1(PA_ROI_QC_t1, "site", "report_status", "row", "site", " ")

comp_by_site_totals <- comp_by_site_totals[-1, ]  #drop blank row
colnames(comp_by_site_totals)[1] <- "Site"


## Need to keep rows as row percenatges but change the total column to a column percent
comp_by_site_totals <- comp_by_site_totals %>%
  mutate(`Total Submitted Mod 2` = `Total Submitted Mod 2` %>%
           str_remove_all(",") %>%                     # Remove commas
           str_remove_all("\\(.*?%\\)") %>%            # Remove percentages in parentheses
           str_trim() %>%                              # Trim whitespace
           as.numeric()) %>%                           # Convert to numeric
  mutate(`Total Submitted Mod 2` = paste0(
    format(`Total Submitted Mod 2`, big.mark = ","),
    " (",
    round(`Total Submitted Mod 2` / `Total Submitted Mod 2`[n()], 2),
    "%)"
  ))

total_rows <- nrow(comp_by_site_totals)
knitr::kable(comp_by_site_totals, 
             format.args = list(big.mark = ","),
             caption='Table 1.1. Current Physical Activity ROI Report Available Status Among Verified Participants That Submitted Module 2', 
             row.names=FALSE,align=c("l","c","c","c"),
             col.names=c("Site", "Available", "Unavailable", "Total Submitted Mod 2"),
             booktabs = TRUE) %>%  
  add_indent(seq(1, total_rows - 1))  %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) %>% 
  footnote(general="Note: Participants who submitted Module 2 will not have a report available only if they are missing all physical activity recreational activity data from Module 2 or if they withdrew prior to submitted Module 2.",
           general_title = "",
           footnote_as_chunk = TRUE, 
           escape = FALSE, 
           threeparttable = TRUE)
```
\newpage
```{r Table 1.2, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}
#### GENERATE TABLE 1.2:  ####

#Filtering to only those who have a report available
PA_ROI_QC_report_available <-PA_ROI_QC %>% filter(report_status == "Available") %>% select(site, report_viewed) 

create_tbl_cross1 <- function(data, row_var, colm_var, row_or_col_pct, row_name, column_name){
  cross__table <- data %>%  
    tbl_cross(
      row = !!sym(row_var),
      col = !!sym(colm_var),
      digits=c(0,2),
      percent = "row",
      missing_text="0 (0.00%)",
      label=list(!!sym(row_var) ~ row_name,
                 !!sym(colm_var) ~ column_name),
      missing="ifany",
      margin_text="Total Report Available") %>%  as_tibble(.name_repair = "minimal") }

comp_by_site_totals <- create_tbl_cross1(PA_ROI_QC_report_available, "site", "report_viewed", "row", "site", " ")

comp_by_site_totals <- comp_by_site_totals[-1, ]  #drop blank row for 'site'
colnames(comp_by_site_totals)[1] <- "Site"

# Apply regex and cleaning steps outside of mutate
# Remove commas
comp_by_site_totals$`Total Report Available` <- gsub(",", "", comp_by_site_totals$`Total Report Available`)
# Remove percentages in parentheses (e.g., (100.00%))
comp_by_site_totals$`Total Report Available` <- gsub("\\(.*?\\%)", "", comp_by_site_totals$`Total Report Available`)
# Trim any leading/trailing spaces
comp_by_site_totals$`Total Report Available` <- trimws(comp_by_site_totals$`Total Report Available`)
# Convert to numeric
comp_by_site_totals$`Total Report Available` <- as.numeric(comp_by_site_totals$`Total Report Available`)

comp_by_site_totals$`Total Report Available` <- paste(format(comp_by_site_totals$`Total Report Available`, big.mark = ","), " (", 
                                                      round(comp_by_site_totals$`Total Report Available` / comp_by_site_totals$`Total Report Available`[nrow(comp_by_site_totals)] * 100, 
                                                            digits = 2), "%)", sep = "")


total_rows <- nrow(comp_by_site_totals)
knitr::kable(comp_by_site_totals , 
             caption='Table 1.2. Current Physical Activity ROI Report Viewed Statuses Among Verified Participants With a Report Available', 
             format.args = list(big.mark = ","),
             row.names=FALSE,align=c("l","c","c","c"),
             col.names=c("Site", "Viewed", "Declined", "Unread", "Total Report Available"),
             booktabs = TRUE) %>%  
  add_indent(seq(1, total_rows - 1))  %>% 
  kable_styling(latex_options = c("scale_down","hold_position")) 


```

```{r Table 1.3, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}
#time from report available to report viewed 
PA_ROI_QC$hours_available_to_viewed <- as.numeric(
  difftime(as.POSIXct(ymd_hms(PA_ROI_QC$d_686238347_d_749055145)),as.POSIXct(ymd_hms(PA_ROI_QC$d_416831581)),units="hours"))
#Generating Table 1.3
Table3 = PA_ROI_QC %>% filter(d_686238347_d_446235715 == 469323437) %>% 
  dplyr::summarize('N'=n(),
                   Min = min(hours_available_to_viewed, na.rm = TRUE),
                   Q1 = quantile(hours_available_to_viewed, 0.25, na.rm = TRUE),
                   Median = median(hours_available_to_viewed, na.rm = TRUE),
                   Mean = mean(hours_available_to_viewed, na.rm = TRUE), 
                   SD = sd(hours_available_to_viewed, na.rm = TRUE),
                   Q3 = quantile(hours_available_to_viewed, 0.75, na.rm = TRUE),
                   'Pct. 90' = quantile(hours_available_to_viewed, 0.90, na.rm = TRUE),
                   Max = max(hours_available_to_viewed, na.rm = TRUE)) 

knitr::kable(Table3,format.args = list(big.mark = ","),
             caption='Table 1.3. Time (in hours) From Physical Activity ROI Report Available to Report Viewed',
             row.names=FALSE, align=c("l",rep("c", 7)),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) %>%
  footnote(general = c("Note:Participants can toggle between report ‘viewed’ and ‘declined’ at any time. We will only capture the first timestamp the report is viewed and the first timestamp the report is declined.", "\n",
                       "Note: There is about a 28.5 to 52.5 hour delay between the report becoming available and participants being notified that they have a report available to view."),
           general_title = "",
           footnote_as_chunk = TRUE, 
           escape = FALSE, 
           threeparttable = TRUE) 

```
\newpage
```{r Table 1.4, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}
#time from report available to report decline 
PA_ROI_QC$hours_available_to_declined <- as.numeric(
  difftime(as.POSIXct(ymd_hms(PA_ROI_QC$d_686238347_d_295732360)),as.POSIXct(ymd_hms(PA_ROI_QC$d_416831581)),units="hours"))

#Generating Table 4
Table4 = PA_ROI_QC %>% filter(d_686238347_d_446235715 == 746038746) %>% 
  dplyr::summarize('N'=n(),
                   Min = min(hours_available_to_declined, na.rm = TRUE),
                   Q1 = quantile(hours_available_to_declined, 0.25, na.rm = TRUE),
                   Median = median(hours_available_to_declined, na.rm = TRUE),
                   Mean = mean(hours_available_to_declined, na.rm = TRUE), 
                   SD = sd(hours_available_to_declined, na.rm = TRUE),
                   Q3 = quantile(hours_available_to_declined, 0.75, na.rm = TRUE),
                   'Pct. 90' = quantile(hours_available_to_declined, 0.90, na.rm = TRUE),
                   Max = max(hours_available_to_declined, na.rm = TRUE)) 

knitr::kable(Table4,format.args = list(big.mark = ","),
             caption='Table 1.4. Time (in hours) From Physical Activity ROI Report Available to Report Declined',
             row.names=FALSE, align=c("l",rep("c", 7)),digits=2, booktabs = TRUE)%>% 
  kable_styling(latex_options = c("scale_down","hold_position")) %>%
  footnote(general = c("Note: Participants can toggle between report ‘viewed’ and ‘declined’ at any time. We will only capture the first timestamp the report is viewed and the first timestamp the report is declined.", "\n",
                       "Note: There is about a 28.5 to 52.5 hour delay between the report becoming available and participants being notified that they have a report available to view."),
           general_title = "",
           footnote_as_chunk = TRUE, 
           escape = FALSE, 
           threeparttable = TRUE) 

```


\newpage
```{r Table 1.5, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}

#Crosstab that looks at baseline data completeness by report viewed status
PA_ROI_QC <- PA_ROI_QC %>% mutate(
  completion = case_when(
    d_100767870=="353358909" & (d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Completed both survey and sample(s)",
    d_100767870=="353358909" ~ "Completed all baseline survey modules 1-4, no baseline samples",
    (d_878865966=="353358909" | d_684635302=="353358909" | d_167958071=="353358909") ~ "Completed any baseline sample, did not complete baseline survey",
    TRUE ~ "Completed neither survey or sample(s)"))

completexviewed <- PA_ROI_QC %>% filter(report_status != "Unavailable") %>% select(completion, report_viewed)
completexviewed2 <- as.data.frame(table(completexviewed$completion, completexviewed$report_viewed))
colnames(completexviewed2) <- c("completion", "report_viewed", "n")

wide_tbl <- completexviewed2 %>%
  pivot_wider(names_from = report_viewed, values_from = n, values_fill = 0) %>%
  mutate(Total = rowSums(across(where(is.numeric)))) %>%
  mutate(completion_status = factor(
    completion,
    levels = c(
      "Completed both survey and sample(s)",
      "Completed any baseline sample, did not complete baseline survey",
      "Completed all baseline survey modules 1-4, no baseline samples",
      "Completed neither survey or sample(s)"
    )
  )) %>%
  arrange(completion_status)

grand_total <- sum(wide_tbl$Total)

formatted_tbl <- wide_tbl %>%
  mutate(across(c(Viewed, Declined, Unread, Total),
                ~ paste0(format(.x, big.mark = ","), " (", sprintf("%.2f", 100 * .x / grand_total), "%)")))

total_counts <- colSums(wide_tbl[, c("Viewed", "Declined", "Unread", "Total")])
total_row <- as.data.frame(t(total_counts))
total_row <- total_row %>%
  mutate(across(everything(), ~ paste0(format(.x, big.mark = ","), " (", sprintf("%.2f", 100 * .x / grand_total), "%)"))) %>%
  mutate(completion = "Total")

final_tbl <- bind_rows(
  formatted_tbl %>% select(completion, Viewed, Declined, Unread,  Total),
  total_row %>% select(completion, Viewed, Declined, Unread,  Total))

knitr::kable(final_tbl,
             caption = "Table 1.5. Physical Activity ROI Report Viewed Status by Baseline Data Completeness Among Participants with a Report Available",
             format.args = list(big.mark = ","),
             col.names = c("Completion", "Viewed", "Declined", "Unread", "Total Available"),
             row.names = FALSE, align = c("l", "c", "c", "c", "c"),
             booktabs = TRUE) %>%
  kable_styling(latex_options = "scale_down") %>%
  add_indent(seq(1, nrow(final_tbl) - 1)) %>%
  landscape()
```

\newpage
```{r Table 1.6, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}
#Baseline Survey Completion Within 30 Days of Viewing or Declining Physical Activity ROI Report Among Participants with a Report Available

### CALCULATE COMPLETED: Those who completed a baseline module (SAS or LAW) within 30 days after completing the PROMIS survey, after viewing or declining the Physical Activity (PA) ROI report
BL_PA_completed <- PA_ROI_QC %>% 
  filter(report_status != "Unavailable" & (report_viewed == "Viewed" | report_viewed == "Declined")) %>%
  mutate(
    SAS = !is.na(d_770257102) &
          as.Date(declined_or_viewed_date) <= as.Date(d_770257102) &
          difftime(as.Date(d_770257102), as.Date(declined_or_viewed_date), units = "days") < 31,

    LAW = !is.na(d_264644252) &
          as.Date(declined_or_viewed_date) <= as.Date(d_264644252) &
          difftime(as.Date(d_264644252), as.Date(declined_or_viewed_date), units = "days") < 31
  ) %>%
  pivot_longer(
    cols = c(SAS, LAW),
    names_to = "after_PA",
    values_to = "is_in_timeframe"
  ) %>%
  filter(is_in_timeframe) %>%
  group_by(after_PA) %>%
  tally()


## CALCULATE ELIGIBLE: Among participants with a PA ROI report who viewed or declined it, how many were eligible to complete each baseline module (SAS or LAW) at that time
# Keep only those who have a report available (report_status != "Unavailable"), and have either viewed or declined it:
BL_time_eligible <- PA_ROI_QC %>% filter(report_status != "Unavailable" & (report_viewed == "Viewed" | report_viewed == "Declined")) %>%
  
# Create 2 variables (SAS and LAW) that includes those who have completed the Background/Health module (d_517311251 not missing), and they either haven’t yet completed SAS/LAW modules, or they viewed/declined the PA report before completing SAS/LAW modules
  mutate( SAS = !is.na(d_517311251) & (is.na(d_770257102) | as.Date(declined_or_viewed_date) <= as.Date(d_770257102)),
          LAW = !is.na(d_517311251) & (is.na(d_264644252) | as.Date(declined_or_viewed_date) <= as.Date(d_264644252))) %>%
  
# Checks whether the participant was eligible to complete the SAS or LAW module at the time of their PA ROI report 
# Reshapes the data to long format, so each row represents either the SAS or LAW eligibility check for each person
  pivot_longer(
    cols = c(SAS, LAW),
    names_to = "after_PA",
    values_to = "is_in_timeframe") %>%

  filter(is_in_timeframe) %>%  
  group_by(after_PA) %>%
  tally()



# Combine tables
after_PA <- cbind(BL_PA_completed, BL_time_eligible)
after_PA <- after_PA[c(2,1), c(1,2,4)] # SAS, LAW row order; drop repeated columns
colnames(after_PA) <- c("Survey", "N_completed", "eligible")

after_PA_table <- after_PA %>%
  mutate(
    Percentage = (N_completed / eligible) * 100,
    N_percent = paste0(
      formatC(N_completed, big.mark = ",", format = "d"),
      " (", round(Percentage, digits = 1), "%)"
    )
  )

# Rename columns manually using colnames(), rename in dplyr was throwing an error
colnames(after_PA_table)[colnames(after_PA_table) == "eligible"] <- "Eligible for Survey"
colnames(after_PA_table)[colnames(after_PA_table) == "N_percent"] <- "N(%)"

# Select the relevant columns
after_PA_table <- after_PA_table %>%
  select(Survey, `N(%)`, `Eligible for Survey`)

knitr::kable(after_PA_table,
             caption = 'Table 1.6. Baseline Survey Completion Within 30 Days of Viewing or Declining Physical Activity ROI Report Among Participants with a Report Available', 
             booktabs=T, linesep = "", row.names=FALSE, align=c("l", "c", "c")) %>% 
  kable_styling(latex_options = "scale_down") %>% 
  footnote(general = "Note: Percentages calculated among those who were eligible but had not yet completed the survey at the time of their PA ROI Report becoming available.", 
           general_title = "",
           footnote_as_chunk = TRUE, 
           escape = FALSE, 
           threeparttable = TRUE)

```

\newpage
```{r Table 1.7, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}
#Table was floating, FloatBarrier prevents that

PA_ROI_QC %>%
  filter(report_status != "Unavailable") %>%
  dplyr::select(guideline_cat, muscle_strengthening) %>% 
  tbl_cross(
    row = guideline_cat,
    col = muscle_strengthening,
    percent = "cell",
    digits = c(0, 1),
    label = list(
      guideline_cat ~ "Physical Activity Guideline",
      muscle_strengthening ~ "Muscle Strengthening"
    ),
    missing = "ifany",
    missing_text = "Unknown"
  ) %>%
  bold_labels() %>%
  modify_header(
    list(
      stat_0 ~ "Total Available",
      stat_1 ~ "No",
      stat_2 ~ "Yes"
    )
  ) %>%
  modify_caption("Table 1.7: Activity Scores Among Verified Participants with a Physical Activity ROI Report Available") %>%
 
 as_kable_extra(escape = FALSE, addtl_fmt = TRUE) %>%
 kable_styling(latex_options = "scale_down") 
```

\newpage
```{r Table 1.8, echo = FALSE, eval = TRUE, results = 'asis', warning = FALSE}
# Filtering to those with a report available
viewedunviewed_filtered <- PA_ROI_QC %>%
  filter(report_status == "Available") %>%
  select(guideline_cat, muscle_strengthening, viewed_vs_unviewed)

# Calculate counts
counts <- viewedunviewed_filtered %>%
  dplyr::count(guideline_cat, muscle_strengthening, viewed_vs_unviewed)

wide_tbl <- counts %>%
  pivot_wider(
    names_from = c(viewed_vs_unviewed, muscle_strengthening),
    values_from = n,
    values_fill = 0,
    names_sep = "_")

# Calculate the totals
wide_tbl <- wide_tbl %>%
  mutate(
    Viewed_Total = Viewed_No + Viewed_Yes,
    Unviewed_Total = Unviewed_No + Unviewed_Yes,
    Total_Available = Viewed_Total + Unviewed_Total)

grand_total <- sum(wide_tbl$Total_Available)

final_tbl <- wide_tbl %>%
  transmute(
    `Physical Activity Guideline` = guideline_cat,
    `No_Viewed` = paste0(format(Viewed_No, big.mark = ","), " (", sprintf("%.1f", 100 * Viewed_No / grand_total), "%)"),
    `No_NotViewed` = paste0(format(Unviewed_No, big.mark = ","), " (", sprintf("%.1f", 100 * Unviewed_No / grand_total), "%)"),
    `Yes_Viewed` = paste0(format(Viewed_Yes, big.mark = ","), " (", sprintf("%.1f", 100 * Viewed_Yes / grand_total), "%)"),
    `Yes_NotViewed` = paste0(format(Unviewed_Yes, big.mark = ","), " (", sprintf("%.1f", 100 * Unviewed_Yes / grand_total), "%)"),
    `Total Available` = paste0(format(Total_Available, big.mark = ","), " (", sprintf("%.1f", 100 * Total_Available / grand_total), "%)"))

total_row <- tibble(
  `Physical Activity Guideline` = "Total",
  `No_Viewed` = paste0(format(sum(wide_tbl$Viewed_No), big.mark = ","), " (", sprintf("%.1f", 100 * sum(wide_tbl$Viewed_No) / grand_total), "%)"),
  `No_NotViewed` = paste0(format(sum(wide_tbl$Unviewed_No), big.mark = ","), " (", sprintf("%.1f", 100 * sum(wide_tbl$Unviewed_No) / grand_total), "%)"),
  `Yes_Viewed` = paste0(format(sum(wide_tbl$Viewed_Yes), big.mark = ","), " (", sprintf("%.1f", 100 * sum(wide_tbl$Viewed_Yes) / grand_total), "%)"),
  `Yes_NotViewed` = paste0(format(sum(wide_tbl$Unviewed_Yes), big.mark = ","), " (", sprintf("%.1f", 100 * sum(wide_tbl$Unviewed_Yes) / grand_total), "%)"),
  `Total Available` = paste0(format(grand_total, big.mark = ","), " (100.0%)"))

final_tbl_with_total <- bind_rows(final_tbl, total_row)

# Renaming columns to avoid duplicates
colnames(final_tbl_with_total) <- c(
  "Physical Activity Guideline",
  "No_Viewed", "No_NotViewed",
   "Yes_Viewed", "Yes_NotViewed",
  "Total_Available"
)



# Get the row number of the total row (last row)
total_row_num <- nrow(final_tbl_with_total)



# Build the formatted table
knitr::kable(
  final_tbl_with_total,
  align = "lcccccc",
  booktabs = TRUE,
  escape = FALSE,
  caption = "Table 1.8: Activity Scores by Report Viewed Status Among Verified Participants with a Physical Activity Report Available",
  col.names = c(
    "Physical Activity Guideline",
    "Viewed", "Not Viewed",  # No
    "Viewed", "Not Viewed",  # Yes
    "Total Available"
  )
) %>%
  kable_styling(latex_options = "scale_down") %>%
  add_header_above(c(" " = 1, "No" = 2, "Yes" = 2, " " = 1)) %>%
  add_header_above(c(" " = 1, "Muscle Strengthening" = 4, " " = 1))

```
